Let There Be Light: \\ Early Observations of the Normal Type Ia Supernova \abc\ \\Show No Evidence for a Dark Period

### 2017-06-14 doc/ms.tex

% \author[0000-0002-8036-8491]{Yi Cao}
% \affil{eScience Institute and Astronomy Department, University of Washington,
%   Seattle, WA 98195}

\author{The Alphabet Friends}
\affil{the intermediate Palomar Transient Factory}

@@

In the case of \abc, the \ion{Ca}{2} IR triplet is very weak, 
likely due to high temperatures in the ejecta. Thus, we
determine the photospheric velocity from the 
\ion{Si}{2}\,$\lambda$6355 line. Visual inspection shows no 
sign of multi-velocity components of \ion{Si}{2}, and that 
\ion{C}{2}\,$\lambda$6580 line overlaps the red
wing of the \ion{Si}{2} line (see Figures~\ref{fig:spec_seq} and \ref{}). Consequently, we model the observed 
spectra between 5,900 and 6,500\,\AA (rest-frame) as the combination 
of two gaussian kernels plus a linear baseline, which
accounts for \ion{Si}{2}, \ion{C}{2} and the
continuum, respectively. The expansion
velocity of \ion{Si}{2} is measured by the central wavelength
of the \ion{Si}{2} Gaussian kernel.

@@

\amiller{Need to thank Rollin for chatting about \ion{C}{2}}

@@

>>>>

% \author{A.~A.~Miller}
% \affil{Center for Interdisciplinary Exploration and Research in Astrophysics (CIERA) and Department of Physics and Astronomy, Northwestern University, 2145 Sheridan Road, Evanston, IL 60208, USA}
% \affil{The Adler Planetarium, Chicago, IL 60605, USA}
%
% \author[0000-0002-8036-8491]{Yi Cao}
% \affil{eScience Institute and Astronomy Department, University of Washington,
%   Seattle, WA 98195}
%
% \author{B.~D.~Bue}
% \affil{Jet Propulsion Laboratory, California Institute of Technology, Pasadena, CA 91109, USA}
%
% \author{M.~M.~Kasliwal}
% \affil{Division of Physics, Mathematics, and Astronomy, California Institute of Technology, Pasadena, CA 91125, USA}
%
% \author{R.~Ferretti}
% \affil{The Oskar Klein Centre, Department of Physics, AlbaNova, SE-106 91 Stockholm, Sweden}
%
% \author{A.~Goobar}
% \affil{The Oskar Klein Centre, Department of Physics, AlbaNova, SE-106 91 Stockholm, Sweden}
%
% \author{R.~R.~Laher}
% \affil{Infrared Processing and Analysis Center, California Institute of Technology, Pasadena, CA 91125, USA}
%
% \author{F.~J.~Masci}
% \affil{Infrared Processing and Analysis Center, California Institute of Technology, Pasadena, CA 91125, USA}
%
% \author{P.~E.~Nugent}
% \affil{Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
% \affil{University of California -- Berkeley, Berkeley, CA 94720, USA}
%
% \author{J.~Sollerman}
% \affil{The Oskar Klein Centre, Department of Astronomy, AlbaNova, SE-106 91 Stockholm, Sweden}
%
% \author{F.~Taddia}
% \affil{The Oskar Klein Centre, Department of Astronomy, AlbaNova, SE-106 91 Stockholm, Sweden}
%
% \author{S. R. Kulkarni}
% \affil{Division of Physics, Mathematics, and Astronomy, California Institute of Technology, Pasadena, CA 91125, USA}
%
\author{The Alphabet Friends}
\affil{the intermediate Palomar Transient Factory}

@@

In the case of \abc, the \ion{Ca}{2} IR triplet is very weak, 
likely due to high temperatures in the ejecta. Thus, we
determine the photospheric velocity from the 
\ion{Si}{2}\,$\lambda$6355 line. Visual inspection shows no 
sign of multi-velocity components of \ion{Si}{2}, and that 
\ion{C}{2}\,$\lambda$6580 line overlaps the red
wing of the \ion{Si}{2} line (see Figures~\ref{fig:spec_seq} and \ref{fig:carbon}). Consequently, we model the observed 
spectra between 5,900 and 6,500\,\AA (rest-frame) as the combination 
of two gaussian kernels plus a linear baseline, which
accounts for \ion{Si}{2}, \ion{C}{2} and the
continuum, respectively. The expansion
velocity of \ion{Si}{2} is measured by the central wavelength
of the \ion{Si}{2} Gaussian kernel.

@@

\amiller{Need to thank Rollin for chatting about \ion{C}{2}}
\amiller{Need to thank Uli, Rahman for chatting about SALT2}

% Observers: Michael West, Gemini observers, J. Cohen, Plant,J.Torres,Jang,Cunningham,Guhathakurta, Ravi, Cao, Yan, Vedantham, Kulkarni, N. Suzuki, Y. Cao, V. Ravi, Walters, Lunnan, Ho, De

@@

Part of this research was carried out at the Jet Propulsion Laboratory, California Institute of Technology, under a contract with the NASA.

DAH, CM, and GH are supported by NSF-1313484. Support for IA was provided by NASA through the Einstein Fellowship Program, grant PF6-170148. This work makes use of observations from the LCO network.
